\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{caption}
\usepackage[position=top]{subcaption}
\usepackage[export]{adjustbox}
\usepackage{array}

\newcommand{\si}[2]{$\mathrm{#1\,#2}$}

\title{Scientific Reports Title to see here}

\author[1,*]{Benjamin Lotter}
\author[1]{Srumika Konde}
\author[1]{Lam Vien Che}
\author[1]{Johnny Nguyen}
\author[1]{Lorenz Maximillian Schneider}
\author[2]{Michael Grau}
\author[1]{Martin Koch}
\author[1]{Peter Lenz}
\affil[1]{Philipps University of Marburg, Department of Physics, Marburg, 35032, Germany}
\affil[2]{University of Münster, Translationale Onkologie, Münster, 48149, Germany}
\affil[*]{corresponding.author@email.example}

%\keywords{Keyword1, Keyword2, Keyword3}

\begin{abstract}
Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations.
\end{abstract}
\begin{document}

\flushbottom
\maketitle
% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
%
%  Click the title above to edit the author information and abstract
%
\thispagestyle{empty}

\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.

\input{introduction.tex}

\section*{Results}

\input{resultsJohnny.tex}

\subsection*{Subsection}

Example text under a subsection. Bulleted lists may be used where appropriate, e.g.

\begin{itemize}
\item First item
\item Second item
\end{itemize}

\subsubsection*{Third-level section}
 
Topical subheadings are allowed.

\section*{Discussion}

The Discussion should be succinct and must not contain subheadings.

\section*{Methods}
\input{methodsJohnny.tex}

\bibliography{D:/bibtex/Microplastics-PaperSDCM}

\section*{Acknowledgements (not compulsory)}

Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.

\section*{Author contributions statement}

B.L. built and evaluated the machine learning models,
S.K., L.V.C. conducted PL measurements,
S.K. provided details on the experiment,
B.L., J.N., L.M.S, analysed the results,
B.L., J.N. wrote on the manuscript, 
J.N., L.M.S., M.G., M.K. and P.L. supervised the project.
All authors reviewed the manuskript.

\section*{Additional information}

To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing interests} (mandatory statement). 

The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

\section*{Supplementary information}
\input{supplementsJohnny.tex}

\end{document}